Pulmonary Exacerbations in CF

### 2024-10-23 Scott Sagel/PEx in CF/analysis_for_yaron.qmd
table 2 p values

```{r}
#| label: tbl-table-1-year
#| tbl-cap: Participant characteristics by year
df %>%
  group_by(sid, year) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  select(year, redcap_data_access_group, sex, race, ethnicity, Genotype) %>%
  tbl_summary(by = year, missing_text = "(Missing)", label = labels)
```

>>>>

```{r}
#| label: tbl-table-1-year
#| tbl-cap: Participant characteristics by year
df %>%
  group_by(sid, year) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  select(year, redcap_data_access_group, sex, race, ethnicity, Genotype) %>%
  tbl_summary(by = year, missing_text = "(Missing)", label = labels) %>%
  add_p() %>%
  separate_p_footnotes()
```
